### 2012-06-19 Weaklensing.tex

Here $\chi^{2}=\underset{i}{\sum}\frac{(O_{i}-E_{i})^{2}}{E_{i}}$
$O_{i}$is the frequency of \{$|\epsilon_{s}|$\},while $E_{i}$is
the expected frequency obtained from P(\textbar{}$\epsilon_{s}|$).

>>>>

Here $\chi^{2}=\underset{i}{\sum}\frac{(O_{i}-E_{i})^{2}}{E_{i}}$
$O_{i}$is the frequency of \{$|\epsilon_{s}|$\} for bin i ,while $E_{i}$is
the expected frequency for bin i which can be obtained from P(\textbar{}$\epsilon_{s}|$).
